18 month progress report

### 2017-03-10 reports/progress_1/progress_1.tex
In progress report, added polynomial fit in shading correction section.

>>>>

To avoid dealing with dead pixels, a method was considered which smoothed the reference images prior to any shading correction parameter estimation. The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically. Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}. The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}. A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit. In the black and grey images, the residuals show a global ring which is very unusual for the black image because it is detecting no x-rays at all. The b/g/w residuals all show vertical stripes. The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects.

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_black.eps}
		\caption{Black}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_grey.eps}
		\caption{Grey}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/polynomial_white.eps}
		\caption{White}
	\end{subfigure}
	\caption{Second order panel-wise surface polynomials fit on the reference images.}
	\label{fig:polynomial_shadingCorrection}
\end{figure*}

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/residual_black.png}
		\caption{Black}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/residual_grey.png}
		\caption{Grey}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width = \textwidth]{../figures/shadingCorrection/residual_white.png}
		\caption{White}
	\end{subfigure}
	\caption{Standardised residuals from the second order panel-wise surface polynomials fit on the reference images.}
	\label{fig:polynomial_residual}
\end{figure*}
